Wolbachia, Toxoplasma and O. Cordyceps: Extreme Host-Manipulating Microbes That Changed the World

### 2015-12-16 paper.tex
Added points for impacts section

>>>>

Scientists have only recently begun doing research on the three microbes discussed above. However, the three microbes mentioned have had a massive impact on the world as we know it.

- Cordyceps has been studied to make an immuno-surpressant drug
- Cordyceps is necessary for keeping bug populations in check
- Toxoplasma has been correlated to a rise in schizophernia
- Wolbachia has made us question evolution
- Infecting insects with Wolbachia causes them to not carry dengue fever
- Targetting Wolbachia to treat filarial infections is effective.
